### 2015-07-06 paper.tex
add rock rate to the diff E,R cut table
add the estimated disk space table

	\end{multicols}
	\begin{center}
		\tabcaption{ \label{tab1} The sum radioactivity singles rates in central detector on different energy and radius threshold }
		\footnotesize
		\begin{tabular*}{170mm}{@{\extracolsep{\fill}} c c c c c c c}
			\toprule  Sum Radioactivity Single Rate(Hz)&E$>$0.1MeV & E$>$0.2MeV & E$>$0.3MeV & E$>$0.4MeV & E$>$0.5MeV & E$>$0.6MeV \\
			\hline
			R$<$10m &142.368  &98.332  &96.9047 &95.9515 &95.2811  &93.7126 \\
			R$<$11m &153.808  &99.1398 &97.5285 &96.4432 &95.6678  &93.8127 \\
			R$<$12m &199.79   &102.354 &100.039 &98.4438 &97.2644  &94.2101 \\
			R$<$13m &249.897  &105.33  &102.395 &100.341 &98.7855  &94.5798 \\
			R$<$14m &249.897  &105.33  &102.395 &100.341 &98.7855  &94.5798 \\
			R$<$15m &289.921  &112.385 &107.156 &103.627 &101.128  &95.4422 \\
			R$<$16m &458.269  &148.923 &131.168 &119.73  &112.381  &99.866  \\
			R$<$17m &540.865  &173.071 &146.688 &129.847 &119.277  &102.776 \\
			\bottomrule
		\end{tabular*}
	\end{center}
	\begin{multicols}{2}

@@

		\section{The disk storage space estimation}
		Now for the JUNO DAQ(Data Acquisition), we have several promising schemes. 
		If the electronic system can do zero suppression, we can just
		save the fired PMT's output information.
		For the normal
		events we assume the average fired PMT number is 1000, the sampling time window 
		is 1 $\mu$s. Each sampling point will occupy 2 bytes disk storage space, so each
		normal event need about 2MByes disk storage space. For the muon events, all the 
		PMTs will be fired. We assume the total PMT number of the central detector is about 
		17746, so each muon event need about 36MBytes.

@@

>>>>

	\end{multicols}
	\begin{center}
		\tabcaption{ \label{tab1} The sum radioactivity singles rates in central detector on different energy and radius threshold }
		\footnotesize
		\begin{tabular*}{170mm}{@{\extracolsep{\fill}} c c c c c c c}
			\toprule  Sum Radioactivity Single Rate(Hz)&E$>$0.1MeV & E$>$0.2MeV & E$>$0.3MeV & E$>$0.4MeV & E$>$0.5MeV & E$>$0.6MeV \\
			\hline
			%rate with out rock rateR$<$10m &142.368  &98.332  &96.9047 &95.9515 &95.2811  &93.7126 \\
			%			R$<$11m &153.808  &99.1398 &97.5285 &96.4432 &95.6678  &93.8127 \\
			%			R$<$12m &199.79   &102.354 &100.039 &98.4438 &97.2644  &94.2101 \\
			%			R$<$13m &249.897  &105.33  &102.395 &100.341 &98.7855  &94.5798 \\
			%			R$<$14m &249.897  &105.33  &102.395 &100.341 &98.7855  &94.5798 \\
			%			R$<$15m &289.921  &112.385 &107.156 &103.627 &101.128  &95.4422 \\
			%			R$<$16m &458.269  &148.923 &131.168 &119.73  &112.381  &99.866  \\
			%			R$<$17m &540.865  &173.071 &146.688 &129.847 &119.277  &102.776 \\
			R$<$10m &146.299  &104.685  &103.623  &102.569  &101.594  &100.510  \\  
			R$<$11m &158.055  &105.545  &104.290  &103.094  &102.007  &100.617  \\
			R$<$12m &205.307  &108.967  &106.975  &105.233  &103.709  &101.043  \\
			R$<$13m &256.797  &112.135  &109.494  &107.261  &105.331  &101.440  \\
			R$<$14m &256.797  &112.135  &109.494  &107.261  &105.331  &101.440  \\
			R$<$15m &297.926  &119.646  &114.585  &110.774  &107.829  &102.365  \\
			R$<$16m &470.923  &158.544  &140.262  &127.987  &119.827  &107.109  \\
			R$<$17m &555.812  &184.252  &156.858  &138.802  &127.180  &110.231  \\

			\bottomrule
		\end{tabular*}
	\end{center}
	\begin{multicols}{2}

@@

		\section{The disk storage space estimation}
		Now for the JUNO DAQ(Data Acquisition), we have several promising schemes. 
		If the electronic system can do zero suppression, we can just
		save the fired PMT's output information.
		For the normal
		events we assume the average fired PMT number is 1000, the sampling time window 
		is 1 $\mu$s. Each sampling point will occupy 2 bytes disk storage space, so each
		normal event need about 2MByes disk storage space. For the muon events, all the 
		PMTs will be fired. We assume the total PMT number of the central detector is about 
		17746, so each muon event need about 36 MBytes.

@@

		In the most possible DAQ scheme, we can do zero suppression in  electronic system, and can't
		do waveform compression. So for the most possible scheme we listed the estimated 
		disk storage space of central detector on different energy and radius threshold in the table.3.

	\end{multicols}
	\begin{center}
		\tabcaption{ \label{tab1} The disk storage space of central detector on different energy and radius threshold }
		\footnotesize
		\begin{tabular*}{170mm}{@{\extracolsep{\fill}} c c c c c c c}
			\toprule  Disk Storage Space(MBytes/s)&E$>$0.1MeV & E$>$0.2MeV & E$>$0.3MeV & E$>$0.4MeV & E$>$0.5MeV & E$>$0.6MeV \\
			\hline
			R$<$10m &400.598  &317.369  &315.246  &313.138  &311.188  &309.020  \\  
			R$<$11m &424.110  &319.089  &316.580  &314.189  &312.013  &309.234  \\
			R$<$12m &518.613  &325.933  &321.949  &318.466  &315.418  &310.087  \\
			R$<$13m &621.595  &332.270  &326.988  &322.522  &318.662  &310.880  \\
			R$<$14m &621.595  &332.270  &326.988  &322.522  &318.662  &310.880  \\
			R$<$15m &703.853  &347.291  &337.170  &329.547  &323.657  &312.730  \\
			R$<$16m &1049.85  &425.088  &388.524  &363.975  &347.654  &322.219  \\
			R$<$17m &1219.60  &476.504  &421.716  &385.604  &362.360  &328.461  \\

			\bottomrule
		\end{tabular*}
	\end{center}
	\begin{multicols}{2}
